Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-29 WSSSPE4_report/WSSSPE4_report.tex
Update WSSSPE4_report.tex

The panel rounded up with a final question about "If you wanted to have the most disastrous effect on scientific software, what one practice would you advise people to keep doing?" A few good responses were discussed, but the biggest laugh went to Mike Croucher who said "Containerize everything!".

>>>>

The panel rounded up with a final question about "If you wanted to have the most disastrous effect on scientific software, what one practice would you advise people to keep doing?"
A few good responses were discussed, but the biggest laugh went to Mike Croucher who said "Containerize everything!"
